When does vapor pressure deficit drive or reduce evapotranspiration?

### 2017-09-29 doc/paper/vpd_et_paper.tex
thinking about completely distroying penman_monteith to clean out all fo the old calc methods that were useless

@@

>>>>

Figure \ref{term3_between} more clearly illustrates differences between PFT. Term 3 can be broken into a scaling (Figure \ref{term3_between}b), and a $D$ term (Figure \ref{term3_between}d). PFTs with smaller uWUE will have larger magnitude scaling, and PFTs with a smaller g1 will have a greater VPD dependence and a larger magnitude $D$ term. When combined into Term 2 - Term 3 (Figure \ref{term3_between}a,c) the consequences are that CRO is the most likely to have a postive $D$ response, and CSH is most likely to have a negative $D$ response. DBF, ENF, and GRA have similiar liklihoods of positive and negative responses, depnding on LAI and VPD. ENF has by far the strongest VPD dependence of response, as observen in Figure \ref{term3_within}.

@@

Now time for full plot as a function of t and rh, then break up into single scaling (g, T), and pft-specific plots of (T, RH), or try 3d maps?
